---
title: "DataScience"
author: "LiuBo"
date: "6/24/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
This is all about how to do data analysis using R.

## 1. Data
This section focus on dealing with data, including Loading Data, Cleaning Data.

### 1.1 Loading Data

### 1.2 Cleaning The Data
In this section, we will remove variables that   
- Have too many NA values.      
- Unrelated variables.  
- Low variance variables.
- Highly correlated variables.

#### Removing NAs
``` {r removing NAs}
# find all variables contain NA values
Train_na_variables <- which(colSums(is.na(Train_Data))==0)
Test_na_variables <- which(colSums(is.na(Test_Data))==0)

# or find variables which has more than 95% NA values
# Train_na_Variables <- sapply(Train_Data, function(x) mean(is.na(x))) > 0.95
# Test_na_Variables <- sapply(Test_Data, function(x) mean(is.na(x))) > 0.95

Training <- Train_Data[,Train_na_variables]
Testing <- Test_Data[,Test_na_variables]

dim(Training);dim(Testing)
```

#### Removing Uncorrelateed Variables
```{r removing uncorrelateed variables}
# find uncorrelated variables
remove = c('X', 'user_name', 'raw_timestamp_part_1', 'raw_timestamp_part_2', 'cvtd_timestamp', 'new_window', 'num_window')

Training <- Training[,-which(names(Training) %in% remove)]
Testing <- Testing[,-which(names(Testing) %in% remove)]

dim(Training);dim(Testing)
```

#### Removing Low Variance Variables
```{r removing low variance variables}
library(caret)
# using nearZeroVar to get those low variance variables, this only can apply on numeric formate.
zeroVar = nearZeroVar(Training[,sapply(Training, is.numeric)],
                     saveMetrics = TRUE)

Training = Training[,zeroVar[, 'nzv']==0]
Testing = Testing[,zeroVar[, 'nzv']==0]

dim(Training);dim(Testing)
```

#### Removing Highly Correlated Variables
```{r}
# using cor to get thee correlation of all numeric variables
corrMatrix <- cor(Training[sapply(Training, is.numeric)])
# set grid
corrDF <- expand.grid(row = 1:dim(corrMatrix)[1], 
                      col = 1:dim(corrMatrix)[2])
# set data to vector so that can be plot
corrDF$correlation <- as.vector(corrMatrix)
# using levelplot to show the relationship between all those variables.
levelplot(correlation ~ row+ col, corrDF)
# find high correlated variables( >90% )
High_cor_var = findCorrelation(corrMatrix, 
                   cutoff = .90, 
                   verbose = TRUE)

Training = Training[, -High_cor_var]
Testing = Testing[, -High_cor_var]

dim(Training);dim(Testing)
```
## 2. Analysis

